\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-29 intro.tex
added a citation
aded text

Distributed systems are notoriously hard to design, implement and test~\cite{cavage2013there, maddox2015test}. This is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with (human) clients.
%
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute. A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases~\cite{gray1986computers, musuvathi2008finding}.

@@

We present three case studies of using \psharp to test production distributed systems for Windows Azure inside Microsoft: a distributed storage management system and a live migration protocol. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time as they did not have an effective way to reproduce the bug and nail down the culprit. \psharp uncovered this bug in a very small setting, which made it easy to examine traces, identify and eventually fix the problem.

@@

\begin{itemize}
\item We present a methodology that allows flexible modeling of the environment of a distributed system using simple language mechanisms.
\item Our infrastructure can test production code written in \csharp, which is a mainstream language.
\item We present three case studies of using \psharp to test production distributed systems, finding bugs that could not be found with traditional testing techniques.
\item ...
\end{itemize}

>>>>

Distributed systems are notoriously hard to design, implement and test~\cite{cavage2013there, laguna2015debugging, maddox2015test}. This is due to many well-known sources of \emph{nondeterminism}~\cite{chandra2007paxos}, such as race conditions in the asynchronous interaction between system components, the use of multithreaded code inside a component, unexpected node failures, unreliable communication channels and data losses, and interaction with (human) clients.
%
All these sources of nondeterminism translate into \emph{exponentially} many execution paths that a distributed system might potentially execute. A bug might hide deep inside one of these paths and only manifest under extremely rare corner cases~\cite{gray1986computers, musuvathi2008finding}.

@@

We present three case studies of using \psharp to test production distributed systems for Windows Azure inside Microsoft: a distributed storage management system and a live migration protocol. Using \psharp, we managed to uncover a very subtle bug that was haunting developers for a long time as they did not have an effective way to reproduce the bug and nail down the culprit. \psharp uncovered this bug in a very small setting, which made it easy to examine traces, identify and eventually fix the problem. We show that bugs in production do not need a large setting to be reproduced; they can be reproduced in small settings with easy to understand traces.

@@

\begin{itemize}
\item We present a methodology that allows flexible modeling of the environment of a distributed system using simple language mechanisms.
\item Our infrastructure can test production code written in \csharp, which is a mainstream language.
\item We present three case studies of using \psharp to test production distributed systems, finding bugs that could not be found with traditional testing techniques.
\item We show that we can reproduce bugs in production systems in a small setting with easy to understand traces.
\end{itemize}

### 2015-08-29 methodology.tex
aded text

Our goal in this work is to \emph{test what is being executed}. To achieve this we developed a new software engineering methodology for testing distributed systems, implemented on top of the \psharp framework. The original \psharp framework is explain in Section~\ref{sec:overview:psharp}, while the new approach is explained in Section~\ref{}.

@@

\psharp~\cite{deligiannis2015psharp} provides an \emph{event-driven asynchronous programming} language and a \emph{systematic concurrency testing} engine for developing highly-reliable distributed systems.

@@

@@

In order to solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a radically different modeling approach. We provide the capability to model the environment of a system using \psharp, and then allow the developer to take advantage of existing language features, such as \emph{method dispatch}, to connect the system under test with the environmental model, and finally test it using the \psharp systematic concurrency testing engine.

@@

\subsection{Using method dispatch for modeling}
\label{sec:method:dd}

@@

\subsection{Abstracting timers}
\label{sec:method:timers}

Distributed systems are often using timers to determine when an event should be fired. For example, in the Azure Storage vNext system, each Extent Node is associated with a timer that fires of a synchronization message every 5 minutes and a heartbeat every 5 seconds. However, when testing to find bugs, these timers should be abstracted away and be triggered nondeterministically.

@@

\subsection{Abstracting node expiration}
\label{sec:method:timers}

>>>>

Our goal in this work is to \emph{test what is being executed}. Our approach involves using \psharp~\cite{deligiannis2015psharp}, a framework that provides: (i) an \emph{event-driven asynchronous programming} language for developing and modeling distributed systems; and (ii) a \emph{systematic concurrency testing} engine that can systematically explore all interleavings between asynchronous event handlers, as well as other nondeterministic events such as failures and timeouts.

@@

@@

\subsection{Overview of our approach}
\label{sec:method:model}

To solve this problem, and allow \psharp to be used for testing legacy distributed systems, we decided to take a radically different approach. We provide the capability to model the environment of a system using \psharp, and then allow the developer to take advantage of existing language features, such as \emph{method dispatch}, to connect the system under test with the environmental model, and finally test it using the \psharp systematic concurrency testing engine.

@@

The environment of a distributed system might consist of other distributed systems and services, clients, operating system timers, as well as libraries for networking or other purposes. To be able to systematically test a distributed system, this environment must be modeled and all the interactions between the environment and the system, as well as all the nondeterminism, must be captured and controlled by the \psharp runtime.

@@

\subsubsection{Using method dispatch for modeling}
\label{sec:method:model:dd}

@@

\subsubsection{Abstracting timers}
\label{sec:method:model:timers}

Abstract timers away so all timing events become message passing: why and how

Distributed systems are often using timers to determine when an event should be send from one component to another. For example, in the Azure Storage vNext system, each Extent Node is associated with a timer that fires of a synchronization message every 5 minutes and a heartbeat every 5 seconds. However, when testing to find bugs, these timers should be abstracted away and be triggered nondeterministically.

@@

\subsubsection{Abstracting node expiration}
\label{sec:method:model:timers}
